### 2016-12-06 paper/chapters/sigmoid_belief_nets.tex
add SBN architecture and small fixes for sbn node

These random variables are interpreted in a bayesian way where each one may be observed, hidden (or latent) or unknown representing different states of knowledge or belief \cite{definetti:1974}.

\begin{figure}[htb]
\centering
\input{media/sbn_node.tikz}
  \caption{VAE architecture (source: VAE paper)}\label{fig:vae_architecture}
\end{figure}
In its most common form, SBNs are comprised by a number of layers where each node in a layer is a sigmoid function of its ancestors:
$$
p(s_i) = \sigma\bigg(\sum_{j<i}W_{j,i}s_j+b_i\bigg)
$$

>>>>

These random variables are interpreted in a bayesian way where each one may be observed, hidden (or latent) or unknown representing different states of knowledge or belief \cite{definetti:1974}.
\begin{figure}[htb]
\centering
\input{media/sbn_architecture}
  \caption{SBN architecture}
  \label{fig:sbn_arch}
  \medskip
  \small
  Sigmoid Belief Network described as a acyclic directed graph where blue nodes indicate hidden variables while red nodes represent observed variables.
  Arrows show stochastic dependency. The dashed arrow indicates that it is possible in the original definition (and in the formula below) to have inter-layer dependencies but they are usually not modelled to simplify the architecture.
\end{figure}

\subsection{Learning}
\begin{figure}[htb]
\centering
\includestandalone[mode=buildnew]{media/sbn_node}
  \caption{Sigmoid Belief Net  architecture}
  \label{fig:sbn_node}
\end{figure}
In its most common form, SBNs are comprised by a number of layers where each node in a layer is a sigmoid function of its ancestors:
$$
p(s_i) = \sigma\bigg(\sum_{j<i}W_{i,j}s_j+b_i\bigg)
$$
